---
title: "exploring"
author: "NAME"
date: "DATE"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the necessary libraries
```{r}

```

Take a look inside your dataset
```{r}

```

### Variation

Perform an analysis of the variation in the "neighbourhood" column. 

```{r}

```

* Which values are the most common? Why?


* Which values are rare? Why? Does that match your expectations?


* Can you see any unusual patterns? What might explain them?



Perform an analysis of the variation in the "room_type" column. 

```{r}

```

* Which values are the most common? Why?


* Which values are rare? Why? Does that match your expectations?


* Can you see any unusual patterns? What might explain them?



Perform an analysis of the variation in the "price" column. Make sure to explore different "binwidth" values in your analysis.

```{r}

```

* Which values are the most common? Why?


* Which values are rare? Why? Does that match your expectations?


* Can you see any unusual patterns? What might explain them?



Perform an analysis of the variation in the "minimum_nights" column. Make sure to explore different "binwidth" values in your analysis.

```{r}

```

* Which values are the most common? Why?


* Which values are rare? Why? Does that match your expectations?


* Can you see any unusual patterns? What might explain them?



Perform an analysis of the variation in the "number_of_reviews" column. Make sure to explore different "binwidth" values in your analysis.

```{r}

```

* Which values are the most common? Why?


* Which values are rare? Why? Does that match your expectations?


* Can you see any unusual patterns? What might explain them?



Perform an analysis of the variation in the "availability_365" column. Make sure to explore different "binwidth" values in your analysis.

```{r}

```

* Which values are the most common? Why?


* Which values are rare? Why? Does that match your expectations?


* Can you see any unusual patterns? What might explain them?


