---
title: "exploring"
author: "Rafael Contreras"
date: "10/29/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the necessary libraries
```{r}

```

Take a look inside your dataset
```{r}

```

### Variation

Perform an analysis of the variation in the "neighbourhood" column. 
```{r}

```

What are your conclusions?

> ans: 

Perform an analysis of the variation in the "room_type" column. 
```{r}

```

What are your conclusions?

> ans:

Perform an analysis of the variation in the "price" column. Make sure to explore different "binwidths" in your analysis.
```{r}

```

What are your conclusions?

> ans:

Perform an analysis of the variation in the "minimum_nights" column. Make sure to explore different "binwidths" in your analysis.
```{r}

```

What are your conclusions?

> ans:

Perform an analysis of the variation in the "number_of_reviews" column. Make sure to explore different "binwidths" in your analysis.
```{r}

```

What are your conclusions?

> ans:

Perform an analysis of the variation in the "availability_365" column. Make sure to explore different "binwidths" in your analysis.
```{r}

```

What are your conclusions?

> ans: